---
title: "Mercedes-Benz Greener Manufacturing - Kaggle Competition"
author: "Akkash K N R"
date: "12 July 2017"
output: html_document
---

### Can you cut the time a Mercedes-Benz spends on the test bench?

https://www.kaggle.com/c/mercedes-benz-greener-manufacturing

In this competition, Daimler is challenging Kagglers to tackle the curse of dimensionality and reduce the time that cars spend on the test bench. Competitors will work with a dataset representing different permutations of Mercedes-Benz car features to predict the time it takes to pass testing. Winning algorithms will contribute to speedier testing, resulting in lower carbon dioxide emissions without reducing Daimler's standards.

#### TRAIN - 0.6243, PUBLIC LB - 0.55167, PRIVATE LB - 0.55003


###Loading the data
```{r}
require(glmnet)
require(ggplot2)

mbTrain <- read.csv('train.csv', header = TRUE)
mbTest <- read.csv('test.csv', header = TRUE)
ID <- mbTest$ID
str(mbTrain[,1:20])

mbTest$y <- NA
mb_TT <- rbind(mbTrain,mbTest)
mbTest$y <- NULL

```

###Analysing Y variable

```{r}
plot(mbTrain$y[order(mbTrain$y)], main="Y variable")
plot(density(mbTrain$y), main="Density plot") #The data is right skewed
```

###Checking for missing data
```{r}
sum(is.na(mbTrain)) #No missing data
sum(is.na(mbTest))
```


###Lets check for the unique
```{r}
col_names <- colnames(mbTrain[,-c(1:2)])

#function to collect features with unique values equal to 1
drop_features <- function(d){
  cc <- colnames(d)
  c <- vector()
  for(i in cc){
    if(length(unique(d[,i])) == 1){
      c <- c(c,i)
    }    
  }
  return(c)
}

train_drop <- drop_features(mbTrain)
test_drop <- drop_features(mbTest[,-2])
final_drop <- c(train_drop, test_drop)
```

###Lets remove the unique values
```{r}
mbTrain[,final_drop] <- NULL
mbTest[,final_drop] <- NULL
```

###Convert the categorical features to numeric
```{r}

LETTERS702 <- tolower(c(LETTERS,sapply(LETTERS,function(x) paste0(x,LETTERS))))
col_names <- setdiff(col_names,final_drop)

cat_col <- c()
for(i in col_names){
  if(class(mbTrain[,i])=='factor'){
    cat_col <- append(cat_col,i,after = length(cat_col))
  }  
}
```


```{r}
for(i in cat_col){
  lvl <- intersect(LETTERS702,unique(mbTrain[,i]))
  label <- match(lvl, LETTERS702)
  mb_TT[[i]]<- as.integer(as.character(factor(mb_TT[[i]],levels=lvl,labels = label)))
}

dTrain <- mb_TT[1:nrow(mbTrain),]
dTest <- mb_TT[4210:nrow(mb_TT),]
dTest$y <- NULL
```

###Implementing xgBoost
```{r}
library(xgboost)

train_x <- dTrain
train_x[] <- lapply(train_x,as.numeric)
train_y <- train_x$y
train_x$y <- NULL

test_x <- dTest
test_x[] <- lapply(test_x,as.numeric)

str(train_x)
newtrain <- xgb.DMatrix(as.matrix(train_x),label=train_y)
newtest <- xgb.DMatrix(as.matrix(test_x))
```

```{r}
xgb_param <- list(colsample_bytree = 0.7, #how many variables to consider for each tree
                  subsample = 0.7, #how much of the data to use for each tree
                  booster = "gbtree",
                  max_depth = 5, #how many levels in the tree
                  eta = 0.02, #shrinkage rate to control overfitting through conservative approach
                  eval_metric = "rmse",
                  objective = "reg:linear",
                  gamma = 2.178051
                  # alpha=0.5,
                  # lambda=0.1938
                  )

xgbcv <- xgb.cv(params = xgb_param, nfold = 10,nrounds = 500, print_every_n = 10,early_stopping_rounds = 20,data = newtrain)
xgbcv

xgb_model <- xgb.train(xgb_param,newtrain,nrounds = xgbcv$best_iteration,print_every_n = 1)
xgb_model

a <- dTrain$y
p <- predict(xgb_model,newtrain)
q<- predict(xgb_model,newtest)
```

```{r}
#train
R2_tr <- 1 - (sum((a-p)^2)/sum((a-mean(a))^2))#0.6243

predictions <- predict(xgb_model,newtest)
sum(is.na(predictions))
```



```{r}
submission <- data.frame('ID'=ID,'y'=predictions)
colnames(submission) <- c('ID','y')
filename <- paste('ak_xgbTree_277_2.178051_0.02',format(Sys.time(),"%Y%m%d%H%M%s"),sep = '_')
#write.csv(submission,paste0(filename,'.csv',collapse = ''),row.names = FALSE)
```



